Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-05-08 manuscript/manuscript.tex
fixed citation

Using another approximation, we can consider what roughly equivalently
reduction in diversity due to background selection is expected, using the
theory of \textcite{Hudson1994-oh,Hudson1995-xc}. Their theory states,

@@

where $U$ is the total genome-wide deleterious mutation rate per generation,
and $R$ is the total recombination map length in Morgans. For \emph{Drosophila
melanogaster} (we currently lack good estimates for \emph{D. simulans}), $R
\approx 3$ Morgans, implying a $G(t)$ of at least 20\% implies $U \gtrsim
0.67$. This is entirely consistent with recent work estimating $U \approx 1.6$
in \emph{D. melanogaster} from longer timescale population genetic data
\parencite{Elyashiv2016-vt} (their estimate of $U$ implies a $G(t) \approx
0.59$, or around 59\% reduction in neutral diversity).

>>>>

Using another approximation, we can consider what roughly equivalently
reduction in diversity due to background selection is expected, using the
theory of Hudson and Kaplan (\citeyear{Hudson1994-oh},
\citeyear{Hudson1995-xc}). Their theory states,

@@

where $U$ is the total genome-wide deleterious mutation rate per generation,
and $R$ is the total recombination map length in Morgans. For \emph{Drosophila
melanogaster} (we currently lack good estimates for \emph{D. simulans}), $R
\approx 3$ Morgans, implying a $G(t)$ of at least 20\% implies $U \gtrsim
0.67$. This is entirely consistent with recent work estimating $U \approx 1.6$
in \emph{D. melanogaster} from longer timescale population genetic data
\parencite{Elyashiv2016-vt} (their estimate of $U$ implies a $G(t) \approx
0.59$, or around 59\% reduction in neutral diversity
